Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-18 MDPI_submission.Rmd
Commit 2023-12-18 11:10

In order to investigate the SDR trends which are the main focus of the
study, we implemented an appropriate aggregation scheme to the
one-minute data to derive a series in coarser time-scales.
To preserve the representativeness of the data we used the following criteria:
<!-- a) for daily mean values we exclude days with less than `r Daily_aggregation_N_lim` valid data points, -->
a) we excluded all days with less than `r 100 * All_daily_ratio_lim`% of the expected daytime measurements,
b) daily means for the clear-sky and cloudy-sky datasets
were calculated only for days with more than
`r 100 * Clear_daily_ratio_lim`% of the expected daytime
measurements identified as clear or cloudy respectively,
c) monthly means were computed from daily means only when at least `r Monthly_aggegation_N_lim` days of the month were available.
To create the daily and monthly climatological means, we averaged the data based on the day of year and calendar month, respectively.
<!-- Seasonal -->
For the seasonal means we averaged the mean daily values in each season (Winter: December - February, Spring: March - May, etc.).
<!-- Deseasonalization -->
Finally, each data set was deseasonalized by subtracting the corresponding climatological annual cycle (daily or monthly) from the actual data.
Finally, to estimate the SZA effect on the SDR trends, the one-minute data were aggregated in $1^\circ$ SZA bins, separately for the morning and afternoon hours, and then were deseasonalized as mentioned above.

@@

For all-sky conditions the brightening effect of SDR (positive trend) is
stronger for large SZAs (Figures\ \ref{fig:szatrends-1} and \ref{fig:szatrends-2})
ranging from about $0.1\,\%/y$ to
about $0.7\,\%/y$.
The trends in the morning and afternoon hours are more or less consistent with small differences, which can be attributed to systematic diurnal variations of aerosols, particularly during the warm period of the year [@Wang2021].

For cloudy-sky conditions (Figure\ \ref{fig:szatrends-3}), we can not discern any significant dependence of the SDR trend with SZA.
For SZAs $16^\circ$ - $50^\circ$, the trends range within about $\pm 0.2\,\%/y$, with a weak statistical significance.
Between $50^\circ$ and $75^\circ$ SZA the trends for the period before noon are stronger and negative, possibly associated with stronger attenuation by clouds under oblique incidence angles.

@@

```{r echo=F, eval=TRUE}
## Prepare table and data
spp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep         = ";",
               header      = TRUE)
spp <- spp[grep("SDR" ,spp$var), ]
spp$slope.sd           <- NULL
spp$slope.ConfInt_0.95 <- NULL
spp$slope.ConfInt_0.99 <- NULL
spp$var                <- NULL

@@

## numeric precision
spp$slope          <- signif(spp$slope,          3)
spp$slope.p        <- signif(spp$slope.p,        3)
spp$slope.stat_sig <- signif(spp$slope.stat_sig, 3)
spp$Rsqrd          <- signif(spp$Rsqrd,          3)
spp$RsqrdAdj       <- NULL
spp$Rsqrd          <- NULL
spp$cor.t          <- NULL
spp$slope.stat_sig <- NULL

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \includegraphics[width=1\linewidth]{./images/SeasonalTrendsTogether3-2} 
        }
        \caption{Linear trends (black lines) of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots).}\label{fig:seasonalALL}
    \end{adjustwidth}
\end{figure}

>>>>

In order to investigate the SDR trends which are the main focus of the
study, we implemented an appropriate aggregation scheme to the
one-minute data to derive a series in coarser time-scales.
To preserve the representativeness of the data we used the following criteria:
<!-- a) for daily mean values we exclude days with less than `r Daily_aggregation_N_lim` valid data points, -->
a) we excluded all days with less than `r 100 * All_daily_ratio_lim`% of the expected daytime measurements,
b) daily means for the clear-sky and cloudy-sky datasets
were calculated only for days with more than
`r 100 * Clear_daily_ratio_lim`% of the expected daytime
measurements identified as clear or cloudy respectively,
c) monthly means were computed from daily means, for all-skies dataset 
means were computed only when at least `r Monthly_aggegation_N_lim` 
days of the month were available.
Seasonal means were derived by averaging the
monthly mean values in each season (winter: December - February, spring:
March - May, etc.).
The daily and monthly climatological means were
derived by averaging the data for each day of year and calendar month,
respectively. The daily and monthly datasets were deseasonalized by
subtracting the corresponding climatological annual cycle (daily or
monthly) from the actual data. Finally, to estimate the SZA effect on
the SDR trends, the one-minute data were aggregated in $1^{\circ}$ SZA
bins, separately for the morning and afternoon hours.

The linear trends were calculated using an autoregressive model
<!-- ([ARIMA......)]{.mark} and were reported together with the 2σ errors. -->
<!-- [For the trends derived from monthly mean data we used an effective -->
<!-- number of observations to calculate the standard error (Sander et al., -->
<!-- 2000) in order to assess the significance of the trends.]{.mark} -->
@Santer2000

@@

For all-sky conditions the brightening effect of SDR (positive trend) is
stronger for large SZAs (Figures\ \ref{fig:szatrends-1} and \ref{fig:szatrends-2})
ranging from about $0.1\,\%/y$ to
about $0.7\,\%/y$.
The trends in the morning and afternoon hours are more or
less consistent with small differences at small SZAs which can be
attributed to effects on clear sky SDR from systematic diurnal patterns
of aerosols during the warm period of the year [@Wang2021]. 
Note that SZAs less than $35^\circ$ can only occur during the warm period of the
year when clear skies are more frequent.

For cloudy-sky conditions (Figure\ \ref{fig:szatrends-3}), we can not discern any significant dependence of the SDR trend with SZA as the variability of irradiance is
dominated by the cloud effects.
For SZAs $25^\circ$ - $75^\circ$, the trends range within about $\pm 0.2\,\%/y$, 
the trends are variable and for most SZAs insignificant ranging between
$0$ and $0.2%\,\%/y$.
Between $50^\circ$ and $75^\circ$ SZA the trends for the period before noon are stronger and negative, possibly associated with stronger attenuation by clouds under oblique incidence angles.

@@

```{r echo=F, eval=TRUE}
## Prepare table and data

# spp <- read.csv("./figures/tbl_longterm_trends_season.dat",
#                strip.white = TRUE,
#                sep         = ";",
#                header      = TRUE)
spp <- read.csv("./figures/tbl_longterm_trends_season_byM.dat",
               strip.white = TRUE,
               sep         = ";",
               header      = TRUE)

spp <- spp[grep("SDR" ,spp$var), ]
spp$slope.sd           <- NULL
spp$slope.ConfInt_0.95 <- NULL
spp$slope.ConfInt_0.99 <- NULL
spp$var                <- NULL

@@

## numeric precision
spp$slope          <- signif(spp$slope,          3)
spp$slope.p        <- signif(spp$slope.p,        3)
spp$slope.stat_sig <- signif(spp$slope.stat_sig, 3)
spp$Rsqrd          <- signif(spp$Rsqrd,          3)
spp$RsqrdAdj       <- NULL
spp$Rsqrd          <- NULL
spp$cor.t          <- NULL
spp$slope.stat_sig <- NULL
spp$N_eff          <- NULL

@@

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \includegraphics[width=1\linewidth]{./images/SeasonalMTrendsTogether3-2}   % Seasonal from Monthly
        }
        \caption{Linear trends (black lines) of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots).}\label{fig:seasonalALL}
    \end{adjustwidth}
\end{figure}

            <!-- % \includegraphics[width=1\linewidth]{./images/SeasonalTrendsTogether3-2}  % Seasonal from Daily -->

### 2023-12-18 MDPI_submission.tex
Commit 2023-12-18 11:10

In order to investigate the SDR trends which are the main focus of the
study, we implemented an appropriate aggregation scheme to the
one-minute data to derive a series in coarser time-scales. To preserve
the representativeness of the data we used the following criteria: a) we
excluded all days with less than 50\% of the expected daytime
measurements, b) daily means for the clear-sky and cloudy-sky datasets
were calculated only for days with more than 60\% of the expected
daytime measurements identified as clear or cloudy respectively, c)
monthly means were computed from daily means only when at least 20 days
of the month were available. To create the daily and monthly
climatological means, we averaged the data based on the day of year and
calendar month, respectively. For the seasonal means we averaged the
mean daily values in each season (Winter: December - February, Spring:
March - May, etc.). Finally, each data set was deseasonalized by
subtracting the corresponding climatological annual cycle (daily or
monthly) from the actual data. Finally, to estimate the SZA effect on
the SDR trends, the one-minute data were aggregated in \(1^\circ\) SZA
bins, separately for the morning and afternoon hours, and then were
deseasonalized as mentioned above.

@@

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & Rsqrd & Pearson cor. & Sky conditions & Days & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5 & mean\_clima & ChangeWpY\\
\midrule
0.3756 & 0.00830 & 0.0911 & All skies & 10250 & 4.727 & 1.96 & 0.000811 & 0.001246 & 387 & 1.452\\
0.0972 & 0.01912 & 0.1383 & Clear skies & 2684 & 0.476 & 1.96 & 0.000194 & 0.000338 & 515 & 0.501\\
0.4077 & 0.00657 & 0.0810 & Cloudy skies & 4937 & 3.566 & 1.96 & 0.000733 & 0.001499 & 290 & 1.181\\
\bottomrule
\end{tabu}
\end{table}

@@

For all-sky conditions the brightening effect of SDR (positive trend) is
stronger for large SZAs (Figures~\ref{fig:szatrends-1} and
\ref{fig:szatrends-2}) ranging from about \(0.1\,\%/y\) to about
\(0.7\,\%/y\). The trends in the morning and afternoon hours are more or
less consistent with small differences, which can be attributed to
systematic diurnal variations of aerosols, particularly during the warm
period of the year \citep{Wang2021}.

For cloudy-sky conditions (Figure~\ref{fig:szatrends-3}), we can not
discern any significant dependence of the SDR trend with SZA. For SZAs
\(16^\circ\) - \(50^\circ\), the trends range within about
\(\pm 0.2\,\%/y\), with a weak statistical significance. Between
\(50^\circ\) and \(75^\circ\) SZA the trends for the period before noon
are stronger and negative, possibly associated with stronger attenuation
by clouds under oblique incidence angles.

@@

Similarly to the long term trends from daily means of SDR discussed
above, we have calculated the trend of the anomalies for the three
different sky conditions, and for each season of the year, using the
corresponding mean monthly values (Figure~\ref{fig:seasonalALL} and
Table~\ref{tab:trendseasontable}). For all-sky conditions the trend in
SDR in winter is the largest (\(0.69\,\%/y\)), followed by the trend in
autumn (\(0.43\,\%/y\), a value close to the long term trend) both
statistically significant above the \(99\,\%\) confidence level. In
spring and summer, the trends are much smaller and of lesser statistical
significance. These seasonal differences indicate a possible relation of
the trends in SDR to trends of clouds during winter and autumn. For
clear-skies, the trend in winter is \(0.36\,\%/y\), larger than for
all-skies (\(0.69\,\%/y\)), which is another indication of a decreasing
trend in cloud optical thickness. Moreover, the trends under clear- and
cloudy-sky conditions are almost complementary to each other,
particularly for winter and autumn, where the signal is stronger. During
spring and summer the statistical significance is very low and the
actual trend too small for a meaningful comparison.

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \includegraphics[width=1\linewidth]{./images/SeasonalTrendsTogether3-2} 
        }
        \caption{Linear trends (black lines) of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots).}\label{fig:seasonalALL}
    \end{adjustwidth}
\end{figure}

@@

\caption{\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\centering}X>{\raggedleft}X}
\toprule
Trend [\%/year] & slope.p & Rsqrd & cor.estimate & Sky condition & Season & N\_eff & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5\\
\midrule
\cellcolor{gray!6}{0.6870} & \cellcolor{gray!6}{0.001330} & \cellcolor{gray!6}{0.31200} & \cellcolor{gray!6}{0.5587342} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{24.08252} & \cellcolor{gray!6}{1e-07} & \cellcolor{gray!6}{2.063524} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-11}
0.1360 & 0.219000 & 0.05150 & 0.2270307 & All skies & Spring & 44.44554 & 1e-07 & 2.014797 & -0.0011 & 0.0015253\\
\cmidrule{1-11}
\cellcolor{gray!6}{0.1230} & \cellcolor{gray!6}{0.096100} & \cellcolor{gray!6}{0.09580} & \cellcolor{gray!6}{0.3094390} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{23.37502} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{2.066823} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-11}
0.4300 & 0.006670 & 0.23500 & 0.4844650 & All skies & Autumn & 21.43236 & 1e-07 & 2.077062 & -0.0011 & 0.0015253\\
\cmidrule{1-11}
\cellcolor{gray!6}{0.3570} & \cellcolor{gray!6}{0.007260} & \cellcolor{gray!6}{0.23000} & \cellcolor{gray!6}{0.4800278} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{18.55573} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{2.096421} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-11}
0.0317 & 0.721000 & 0.00445 & 0.0667338 & Clear skies & Spring & 21.33345 & 0e+00 & 2.077636 & -0.0011 & 0.0015253\\
\cmidrule{1-11}
\cellcolor{gray!6}{-0.0931} & \cellcolor{gray!6}{0.007770} & \cellcolor{gray!6}{0.22700} & \cellcolor{gray!6}{-0.4764646} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{25.12298} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{2.059027} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-11}
0.1100 & 0.308000 & 0.03710 & 0.1926085 & Clear skies & Autumn & 23.96832 & 0e+00 & 2.064043 & -0.0011 & 0.0015253\\
\cmidrule{1-11}
\cellcolor{gray!6}{0.8250} & \cellcolor{gray!6}{0.000123} & \cellcolor{gray!6}{0.41500} & \cellcolor{gray!6}{0.6439160} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{14.68318} & \cellcolor{gray!6}{1e-07} & \cellcolor{gray!6}{2.135462} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-11}
0.0942 & 0.425000 & 0.02210 & 0.1485860 & Cloudy skies & Spring & 35.40650 & 1e-07 & 2.029275 & -0.0011 & 0.0015253\\
\cmidrule{1-11}
\cellcolor{gray!6}{-0.0983} & \cellcolor{gray!6}{0.414000} & \cellcolor{gray!6}{0.02400} & \cellcolor{gray!6}{-0.1548507} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{37.66778} & \cellcolor{gray!6}{1e-07} & \cellcolor{gray!6}{2.024981} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-11}
0.1950 & 0.460000 & 0.01960 & 0.1401398 & Cloudy skies & Autumn & 28.41812 & 2e-07 & 2.047050 & -0.0011 & 0.0015253\\
\bottomrule
\end{tabu}
\end{table}

@@

The observed brightening on SDR over Thessaloniki is dependent on SZA
(larger SZAs lead to stronger brightening). The trend is also dependent
on season, with winter showing the strongest statistically significant
trend of \(0.69\) and \(0.36\,\%/y\) for all- and clear-skies,
respectively, in contrast to spring and summer. The trends for autumn
are also significant but smaller ( \(0.43\) and \(0.11\,\%/y\) for all-
and clear-skies, respectively). Our findings are in agreement with other
studies for the region.

>>>>

In order to investigate the SDR trends which are the main focus of the
study, we implemented an appropriate aggregation scheme to the
one-minute data to derive a series in coarser time-scales. To preserve
the representativeness of the data we used the following criteria: a) we
excluded all days with less than 50\% of the expected daytime
measurements, b) daily means for the clear-sky and cloudy-sky datasets
were calculated only for days with more than 60\% of the expected
daytime measurements identified as clear or cloudy respectively, c)
monthly means were computed from daily means, for all-skies dataset
means were computed only when at least 20 days of the month were
available. Seasonal means were derived by averaging the monthly mean
values in each season (winter: December - February, spring: March - May,
etc.). The daily and monthly climatological means were derived by
averaging the data for each day of year and calendar month,
respectively. The daily and monthly datasets were deseasonalized by
subtracting the corresponding climatological annual cycle (daily or
monthly) from the actual data. Finally, to estimate the SZA effect on
the SDR trends, the one-minute data were aggregated in \(1^{\circ}\) SZA
bins, separately for the morning and afternoon hours.

The linear trends were calculated using an autoregressive model
\citet{Santer2000}

@@

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Trend [\%/year] & Pearson cor. & Sky conditions & Days & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5 & mean\_clima & ChangeWpY\\
\midrule
0.3756 & 0.0911 & All skies & 10250 & 4.727 & 1.96 & 0.000811 & 0.001246 & 387 & 1.452\\
0.0972 & 0.1383 & Clear skies & 2684 & 0.476 & 1.96 & 0.000194 & 0.000338 & 515 & 0.501\\
0.4077 & 0.0810 & Cloudy skies & 4937 & 3.566 & 1.96 & 0.000733 & 0.001499 & 290 & 1.181\\
\bottomrule
\end{tabu}
\end{table}

@@

For all-sky conditions the brightening effect of SDR (positive trend) is
stronger for large SZAs (Figures~\ref{fig:szatrends-1} and
\ref{fig:szatrends-2}) ranging from about \(0.1\,\%/y\) to about
\(0.7\,\%/y\). The trends in the morning and afternoon hours are more or
less consistent with small differences at small SZAs which can be
attributed to effects on clear sky SDR from systematic diurnal patterns
of aerosols during the warm period of the year \citep{Wang2021}. Note
that SZAs less than \(35^\circ\) can only occur during the warm period
of the year when clear skies are more frequent.

For cloudy-sky conditions (Figure~\ref{fig:szatrends-3}), we can not
discern any significant dependence of the SDR trend with SZA as the
variability of irradiance is dominated by the cloud effects. For SZAs
\(25^\circ\) - \(75^\circ\), the trends range within about
\(\pm 0.2\,\%/y\), the trends are variable and for most SZAs
insignificant ranging between \(0\) and \(0.2%\,\%/y\). Between
\(50^\circ\) and \(75^\circ\) SZA the trends for the period before noon
are stronger and negative, possibly associated with stronger attenuation
by clouds under oblique incidence angles.

@@

Similarly to the long term trends from daily means of SDR discussed
above, we have calculated the trend of the anomalies for the three
different sky conditions, and for each season of the year, using the
corresponding mean monthly values (Figure~\ref{fig:seasonalALL} and
Table~\ref{tab:trendseasontable}). For all-sky conditions the trend in
SDR in winter is the largest (\(0.7\,\%/y\)), followed by the trend in
autumn (\(0.42\,\%/y\), a value close to the long term trend) both
statistically significant above the \(99\,\%\) confidence level. In
spring and summer, the trends are much smaller and of lesser statistical
significance. These seasonal differences indicate a possible relation of
the trends in SDR to trends of clouds during winter and autumn. For
clear-skies, the trend in winter is \(0.4\,\%/y\), larger than for
all-skies (\(0.7\,\%/y\)), which is another indication of a decreasing
trend in cloud optical thickness. Moreover, the trends under clear- and
cloudy-sky conditions are almost complementary to each other,
particularly for winter and autumn, where the signal is stronger. During
spring and summer the statistical significance is very low and the
actual trend too small for a meaningful comparison.

\begin{figure}[h!]
    \begin{adjustwidth}{-\extralength}{0cm}
        {\centering 
            \includegraphics[width=1\linewidth]{./images/SeasonalMTrendsTogether3-2}   % Seasonal from Monthly
        }
        \caption{Linear trends (black lines) of monthly mean anomalies of SDR by season (rows of plots) for the three sky conditions (columns of plots).}\label{fig:seasonalALL}
    \end{adjustwidth}
\end{figure}

\begin{verbatim}
        <!-- % \includegraphics[width=1\linewidth]{./images/SeasonalTrendsTogether3-2}  % Seasonal from Daily -->
\end{verbatim}

@@

\caption{\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\centering}X}
\toprule
Trend [\%/year] & slope.p & cor.estimate & Sky condition & Season & t\_eff & t\_eff\_cri & conf\_2.5 & conf\_97.5\\
\midrule
\cellcolor{gray!6}{0.7000} & \cellcolor{gray!6}{0.002770} & \cellcolor{gray!6}{0.5353286} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{2e-07} & \cellcolor{gray!6}{2.060774} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-9}
0.1070 & 0.371000 & 0.1663281 & All skies & Spring & 1e-07 & 2.011940 & -0.0011 & 0.0015253\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.1050} & \cellcolor{gray!6}{0.175000} & \cellcolor{gray!6}{0.2543074} & \cellcolor{gray!6}{All skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{2.050358} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-9}
0.4230 & 0.009390 & 0.4663313 & All skies & Autumn & 1e-07 & 2.074143 & -0.0011 & 0.0015253\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.3950} & \cellcolor{gray!6}{0.000515} & \cellcolor{gray!6}{0.5956771} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{2.116842} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-9}
0.0591 & 0.497000 & 0.1267072 & Clear skies & Spring & 0e+00 & 2.069495 & -0.0011 & 0.0015253\\
\cmidrule{1-9}
\cellcolor{gray!6}{-0.0540} & \cellcolor{gray!6}{0.106000} & \cellcolor{gray!6}{-0.3013716} & \cellcolor{gray!6}{Clear skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{0e+00} & \cellcolor{gray!6}{2.035625} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-9}
0.0539 & 0.366000 & 0.1712676 & Clear skies & Autumn & 0e+00 & 2.119437 & -0.0011 & 0.0015253\\
\cmidrule{1-9}
\cellcolor{gray!6}{0.7590} & \cellcolor{gray!6}{0.000665} & \cellcolor{gray!6}{0.5861420} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Winter} & \cellcolor{gray!6}{1e-07} & \cellcolor{gray!6}{2.077321} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-9}
0.0621 & 0.593000 & 0.0997924 & Cloudy skies & Spring & 1e-07 & 2.026109 & -0.0011 & 0.0015253\\
\cmidrule{1-9}
\cellcolor{gray!6}{-0.0789} & \cellcolor{gray!6}{0.560000} & \cellcolor{gray!6}{-0.1109085} & \cellcolor{gray!6}{Cloudy skies} & \cellcolor{gray!6}{Summer} & \cellcolor{gray!6}{1e-07} & \cellcolor{gray!6}{2.013800} & \cellcolor{gray!6}{-0.0011} & \cellcolor{gray!6}{0.0015253}\\
\cmidrule{1-9}
0.1910 & 0.384000 & 0.1648275 & Cloudy skies & Autumn & 1e-07 & 2.055579 & -0.0011 & 0.0015253\\
\bottomrule
\end{tabu}
\end{table}

@@

The observed brightening on SDR over Thessaloniki is dependent on SZA
(larger SZAs lead to stronger brightening). The trend is also dependent
on season, with winter showing the strongest statistically significant
trend of \(0.7\) and \(0.4\,\%/y\) for all- and clear-skies,
respectively, in contrast to spring and summer. The trends for autumn
are also significant but smaller ( \(0.42\) and \(0.054\,\%/y\) for all-
and clear-skies, respectively). Our findings are in agreement with other
studies for the region.
